A Survey on Ordered Binary Decision Diagrams

### 2015-09-13 paper.tex
Fix wording

However, this would result in an algorithm having a time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} (\textit{ITE})
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

\noindent
The ITE operator $ITE(x, y_1, y_2)$ chooses $y_1$ if $x$ evaluates to true and
$y_2$ otherwise. Computing $ITE(x, y_1, y_2)$ is accomplished by utilizing the
following recursive form:

>>>>

This would result in an algorithm having a worst case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} (\textit{ITE})
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

\noindent
For a given node $x$, the ITE operator $ITE(x, hi(x), lo(x))$ chooses $hi(x)$ if
$x$ evaluates to true and $lo(x)$ otherwise. Computing $ITE(x, hi(x), lo(x))$ is
accomplished by utilizing the following recursive form:
\begin{center}
$
ITE(x, hi(x), lo(x)) =
(x, ITE(), ITE())
$
\end{center}
